### 2017-09-06 Documents/bootcamp_syllabus.tex
Updated Syllabus

Everything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{https://nyu.data-bootcamp.com/undergrad_outline/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

@@

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them --- they're good practice ---
but your grade will be based on the best two. We find that people who finish these assignments
tend to keep up with the material better and these are easy points to get in terms of grades.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

@@

Python is not something you can learn from reading a book and attending lectures.
You need to {\bf write programs\/} ---
the more the better --- to understand how they work.
Think about how you'd learn to play basketball or soccer;
reading and listening to lectures aren't enough, you need to do it.
We'll do a lot of programming in class, but it's {essential\/} that you
follow up outside of class.
Here's how.

>>>>

Everything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{https://nyu.data-bootcamp.com/undergrad_outline/}
\end{center}
\vspace{-0.15in}

\textbf{Note we will NOT use NYU Classes.}

The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.

@@

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them|they're good practice|
but your grade will be based on the best two. We find that people who finish these assignments
tend to keep up with the material better and these are easy points to get in terms of grades.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

@@

Python is not something you can learn from reading a book and attending lectures.
You need to {\bf write programs\/}|
the more the better|to understand how they work.
Think about how you'd learn to play basketball or soccer;
reading and listening to lectures aren't enough, you need to do it.
We'll do a lot of programming in class, but it's {essential\/} that you
follow up outside of class.
Here's how.
